\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape NAVNEET PRAJAPATI} \\ \vspace{1pt}
    Gurugram,Haryana \\ \vspace{1pt}
    \small 
    
    \href{tel:+91 7271088606}{ \raisebox{-0.1\height}\faPhone\ \underline{+91 7271088606} ~} \href{navneetprajapati26@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{navneetprajapati26@gmail.com}~}
    \href{https://www.linkedin.com/in/navneetprajapati26/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}} ~
    \href{https://github.com/navneetprajapati26}{\raisebox{-0.2\height}\faGithub\ \underline{github}} ~
    \href{https://www.youtube.com/@asyncapp}{\raisebox{-0.2\height}\faYoutube\ \underline{Youtube}} ~
    \href{https://navneet.asyncapps.com/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    
    \vspace{-5pt}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rajkiya Engineering College Sonbhadra}{07 2020 -- 07 2024}
      {Bachelor of technology (Computer science) }{Sonbhadra, India}
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {SDS Intercollege Varanasi}{2018 -- 2020}
      {intermediate (PCM)  }{Varanasi,India}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Data Structures \& Algorithms
                \item Operating Systems
                % \item Network Security
                \item DBMS
                \item OOPS Concept
                \item Backend Development 
                \item Cross platform Development
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{Dart,Go,JavaScript,Python, Java,}} \\
     \textbf{\normalsize{Developer Tools:}}{ \normalsize{VS Code,Android Studio,GoLand,Intellij}} \\
     \textbf{\normalsize{Technologies/Frameworks:}}{\normalsize{ Flutter, Bloc, Riverpod, Provider, GetX, GIN, GORM, Postgresql, MySQL, Linux, NodeJS, ExpressJS, Git, MongoDB, DynamoDB, Serverless framework, AWS lambda, Firebase, GitHub,}} \\
    }}
 \end{itemize}
 \vspace{-15pt}




%-----------EXPERIENCE-----------
\section{WORK EXPERIENCES }

\resumeSubHeadingListStart

    \resumeSubheading
      {Internshala\href{https://internshala.com/}{\raisebox{-0.1\height}\faLink }}{Feb 2024 - Present} 
      {\underline{Associate Software Engineer}}{(On-site) Gurugram}
      \resumeItemListStart
        \resumeItem{\normalsize{Promoted from intern to full-time role. Achievements include:}}
        \resumeItem{\normalsize{Designed code architecture for iOS Flutter projects implementing Riverpod with clean architecture}}
        \resumeItem{\normalsize{Developed centralized cookie management system for API interactions using Dio}}
        \resumeItem{\normalsize{Implemented background API calling system and background processing infrastructure}}
        \resumeItem{\normalsize{Built common API calling framework with standardized response handling and force update functionality}}
        \resumeItem{\normalsize{Successfully delivered purchase module for iOS and implemented numerous UI components with state management}}
        \resumeItem{\normalsize{\textbf{Technologies: Flutter (Riverpod), clean architecture, Dio, iOS development}}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

   \resumeSubHeadingListStart

    \resumeSubheading
      {Visario\href{https://www.myvisario.com/}{\raisebox{-0.1\height}\faLink }}{Sep 2023 - Feb 2024} 
      {\underline{Full Stack Developer}}{(Remote) Amsterdam-Netherlands}
      \resumeItemListStart
        \resumeItem{\normalsize{Developed full-stack user onboarding process with both frontend (Flutter) and backend (Go) implementation}}
        \resumeItem{\normalsize{Built end-to-end visa application flow interface with seamless user experience and form validation}}
        \resumeItem{\normalsize{Integrated Razorpay payment gateway for secure financial transactions within the application}}
        \resumeItem{\normalsize{\textbf{Technologies: Flutter (Riverpod), Go, AWS (Cognito, Lambda, API Gateway, DynamoDB, S3 bucket)}}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

 \resumeSubHeadingListStart
    \resumeSubheading
      {Subspace\href{https://subspace.money/}{\raisebox{-0.1\height}\faLink }}{Oct 2023 - Dec 2023} 
      {\underline{SDE Internship}}{(Remote) Bengaluru}
      \resumeItemListStart
        \resumeItem{\normalsize{Here my role is Development of applications using  \textbf{Technologies: Flutter (Bloc), flutter-Animation, GraphQL API integration Node.js, }}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd



   \resumeSubHeadingListStart

    \resumeSubheading
      {AsyncApp YouTube \href{https://www.youtube.com/@asyncapp}{\raisebox{-0.1\height}\faLink }}{ Feb 2023 - Present} 
      {\underline{Educator}}{My own YouTube chanel}
      \resumeItemListStart
        \resumeItem{\normalsize{Creating and publishing educational content in video format.
Leading the development of new projects and documentation.
 \textbf{Flutter, Go, Node.js, AWS}}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

   \resumeSubHeadingListStart

    \resumeSubheading
      {GradClabs \href{https://gradclubs.app/}{\raisebox{-0.1\height}\faLink }}{ Jun 2023 - Aug 2023} 
      {\underline{Internship}}{(Remote) Canda}
      \resumeItemListStart
        \resumeItem{\normalsize{Here my role was developed a website using Flutter.
Implemented a full Chatbot system and WhatsApp automation used technology: \textbf{ Flutter (Provider), Node.js, AWS (ES2 Instance), Firebase (functions, hosting, storage)
.}}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

   \resumeSubHeadingListStart

    \resumeSubheading
      {Sofodel \href{https://www.sofodel.com/}{\raisebox{-0.1\height}\faLink }}{Oct 2022 - Jun 2023} 
      {\underline{Internship}}{(Remote)Delhi, India}
      \resumeItemListStart
        \resumeItem{\normalsize{Here my role was Focused on UI development.
Assisted in the building and deployment of projects. using
 \textbf{Flutter (Provider, GetX), Node.js}}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}


%-----------PROJECTS-----------
\section{PROJECTS}
\vspace{-3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\large{\underline{Restaurant Management Suite}}} $|$ \large{\underline{Go (GIN, GORM), PostgreSQL, Flutter, React}}}{Present}
\resumeItemListStart
\resumeItem{\normalsize{Developing end-to-end solution with multi-outlet management, tableside ordering, integrated POS, staff management, and automated inventory control.}}
\resumeItem{\normalsize{Designed with modular architecture using Go backend API, Flutter admin dashboard, and React customer-facing interfaces.}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\href{https://play.google.com/store/apps/details?id=com.asyncapps.parcha.app}{\textbf{\large{\underline{Parcha (Invoice \& Inventory System)}}} \href{https://play.google.com/store/apps/details?id=com.asyncapps.parcha.app}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Flutter (Riverpod), SQLite, IndexDB}}}{12 2024 -- 01 2025}
\resumeItemListStart
\resumeItem{\normalsize{Built cross-platform solution for complete shop management with inventory tracking, customer database, and customizable invoice generation.}}
\resumeItem{\normalsize{Implemented UPI-integrated payment QR codes on PDF invoices, multi-template support, and cross-platform storage solution working across desktop, mobile, and web.}}
\resumeItem{\textcolor{accent}{\href{https://play.google.com/store/apps/details?id=com.asyncapps.parcha.app}{\underline{\normalsize{Live App}}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\href{https://pub.dev/packages/utility_flutter}{\textbf{\large{\underline{Utility Flutter for Pub.dev}}} \href{https://pub.dev/packages/utility_flutter}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Flutter, Dart, HTTP, Shared Preferences}}}{10 2023}
\resumeItemListStart
\resumeItem{\normalsize{Open-source package simplifying HTTP and shared preferences operations in Flutter. Features include default headers, request timeouts, standardized error responses, and local variable storage.}}
\resumeItem{\textcolor{accent}{\href{https://pub.dev/packages/utility_flutter}{\underline{\normalsize{See on Pub.dev}}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\href{https://play.google.com/store/apps/details?id=com.mylight.shyampatt}{\textbf{\large{\underline{Shyampatt (Painting Canvas and Whiteboard)}}} \href{https://play.google.com/store/apps/details?id=com.mylight.shyampatt}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Flutter, Riverpod, Hive DB, CustomPainter}}}{09 2023}
\resumeItemListStart
\resumeItem{\normalsize{Digital whiteboard for Android TV/Windows PC. Drawing platform for Android/iOS with multiple drawing saves and children's templates.}}
\resumeItem{\textcolor{accent}{\href{https://play.google.com/store/apps/details?id=com.mylight.shyampatt}{\underline{\normalsize{Live App}}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\href{https://youtu.be/aWNm1VBFQII?si=b1k3bZqeIRd4xkF6}{\textbf{\large{\underline{Full-Stack Blogging Platform}}} \href{https://youtu.be/aWNm1VBFQII?si=b1k3bZqeIRd4xkF6}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Flutter, Node.js}}}{08 2023}
\resumeItemListStart
\resumeItem{\normalsize{User authentication and blog management (post, edit, delete). Cross-user blog visibility. Accompanied by instructional YouTube series.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/navneetprajapati26/file_reducer}{\textbf{\large{\underline{File Size Reducer}}} \href{https://github.com/navneetprajapati26/file_reducer}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{BLoC, Go Routes, Express.js}}}{09 2023}
\resumeItemListStart
\resumeItem{\normalsize{Reduces file quality as per user preference and retrieves files post-compression.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/navneetprajapati26/chat_app}{\textbf{\large{\underline{Real-Time Chatting Application}}} \href{https://github.com/navneetprajapati26/chat_app}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{GetX, Socket.io}}}{07 2023}
\resumeItemListStart
\resumeItem{\normalsize{Supports real-time group chats with user-specific nicknames.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{link.co}{\textbf{\large{\underline{WhatsApp AI Automation}}} \href{link.co}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{whatsapp-web.js, Axios, GPT API, AWS EC2}}}{06 2023}
\resumeItemListStart
\resumeItem{\normalsize{Transforms a regular WhatsApp number into an AI-powered chatbot.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://play.google.com/store/apps/details?id=com.mylight.snake_game}{\textbf{\large{\underline{Scheduled Email Sending API}}} \href{https://play.google.com/store/apps/details?id=com.mylight.snake_game}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{NodeMailer, Node-cron}}}{05 2023}
\resumeItemListStart
\resumeItem{\normalsize{Allows customizable email scheduling with user-defined intervals.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://play.google.com/store/apps/details?id=com.mylight.wallApp}{\textbf{\large{\underline{Dynamic Wallpaper Application}}} \href{https://play.google.com/store/apps/details?id=com.mylight.wallApp}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Provider, Wallpaper API}}}{04 2023}
\resumeItemListStart
\resumeItem{\normalsize{Features extensive wallpaper browsing, direct setting, and search functionality.}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://play.google.com/store/apps/details?id=com.mylight.snake_game}{\textbf{\large{\underline{Classic Snake Game}}} \href{https://play.google.com/store/apps/details?id=com.mylight.snake_game}{\raisebox{-0.1\height}\faLink }} $|$ \large{\underline{Flutter}}}{11 2022}
\resumeItemListStart
\resumeItem{\normalsize{Classic snake game with real-time score and high-score tracking.}}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-12pt}
%-----------INVOLVEMENT---------------
\section{EXTRACURRICULAR}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Team Leadership}{} 
      {}{} 
      \resumeItemListStart
        \resumeItem{\normalsize{I am class representative of my branch in my college, and also I am head of skit department in our college.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
 \vspace{-11pt}
 


\end{document}
